# ToothGrowth Data Analysis

### Elliot Smith

## Overview

In this project, I will be performing some analyses on the ToothGrowth 
dataset. Using techniques learned in the course, I will draw some conclusions 
on this dataset.

## Load the Date and Basic Analyses

First I will begin by loading the ggplot2 package:

```{r}
library(ggplot2)
```

The following code will load the data for us. The basic analysis will shed 
some light into why I chose the dose variable to be a factor:

```{r}
data(ToothGrowth)
data <- ToothGrowth
data$dose <- as.factor(data$dose)
```

Now for a basic analysis:

```{r}
str(data)
```

```{r}
summary(data)
```

```{r}
ggplot(data=data, aes(x=dose, y=len, fill=supp)) +
geom_bar(stat="identity",) +
facet_grid(. ~ supp)
```

Some things of notes from our basic analysis:

* The dose variable is best set as a factor of 3 levels: 0.5, 1, 2
* The max value of len is 33.9, while the minimum value is 4.2
* len has a Mean of 18.81 and a Median of 19.25, very close indeed!
* There exists a positive correlation between dose levels and tooth length

## Advanced Analysis

### First Analysis

```{r}
t.test(len ~ supp, data=data)
```

Summary: 

There certainly appears to be concrete evidence that across all 
dosage levels, OJ is superior to VC in regards to an increase in tooth length. 
However, an interesting next step would be to break the t-test out by levels 
of dosage.

### Second Analysis

```{r}
t.test(len ~ supp, data=data[data$dose==0.5, 1:3])
```

```{r}
t.test(len ~ supp, data=data[data$dose==1, 1:3])
```

```{r}
t.test(len ~ supp, data=data[data$dose==2, 1:3])
```

Summary: 

Our independant t-tests at different levels of dosage shows us a few 
interesting pieces of information. First of all, there is a clear correlation 
between increase in dose and increase in tooth length. In addition, across all 
dosage levels, OJ is clearly superior to VC. However, that affect is much more 
material in the lower doses; once the dose is at level 2, the affect is almost 
the same. 

## Conclusions and Assumptions

### Conclusions

* Based on the dataset provided, it is safe to say that increasing the dose 
will result in an increase in the tooth length (len)
* However, the type of supplement used has a much smaller impact than the dose 
of the supplement
* OJ is much more affective at lower dosage levels than is VC

### Assumptions

* The sample is representative of the population
* The variances of the two populations are different

