# ToothGrowth Data Analysis

### Elliot Smith

## Overview

In this project, I will be performing some analyses on the ToothGrowth 
dataset. Using techniques learned in the course, I will draw some conclusions 
on this dataset.

## Load the Date and Basic Analyses

First I will begin by loading the ggplot2 package:

```{r}
library(ggplot2)
```

The following code will load the data for us. The basic analysis will shed some light into why I chose the dose variable to be a factor:

```{r}
data(ToothGrowth)
data <- ToothGrowth
data$dose <- as.factor(data$dose)
```

Now for a basic analysis:

```{r}
str(data)
```

```{r}
summary(data)
```

```{r}
ggplot(data=data, aes(x=dose, y=len, fill=supp)) +
geom_bar(stat="identity",) +
facet_grid(. ~ supp)
```

Some things of notes from our basic analysis:
* The dose variable is best set as a factor of 3 levels: 0.5, 1, 2
* The max value of len is 33.9, while the minimum value is 4.2
* len has a Mean of 18.81 and a Median of 19.25, very close indeed!
* There exists a positive correlation between dose levels and tooth length

## Advanced Analysis

### First Analysis

```{r}
t.test(len ~ supp, data=data)
```

Summary:

### Second Analysis

```{r}
t.test(len ~ supp, data=data[data$dose==0.5, 1:3])
```

```{r}
t.test(len ~ supp, data=data[data$dose==1, 1:3])
```

```{r}
t.test(len ~ supp, data=data[data$dose==2, 1:3])
```

Summary:

## Conclusions and Assumptions

### Conclusions

* Based on the dataset provided, it is safe to say that increasing the dose 
will result in an increase in the tooth length (len)
* However, the type of supplement used has a much smaller impact than the dose 
of the supplement

### Assumptions

* The sample is representative of the population
* The variances of the two populations are different

