# Exponential Distribution in R and the Central Limit Theorem

### Elliot Smith



## Overview

In this project, I will be investigating the exponential distribution in R and 
will compare it to the Central Limit Theorem. To do this, I will use the 
accompanying R functionality to explore this relationship focusing on the 
distribution of 40 exponentials. I will be running a thousand simulations to 
clearly enforce my findings.

## Simulations

First, I will begin by setting my assigned constant values and loading the necessary packages:

```{r}
library(ggplot2)
```

```{r}
lambda <- 0.2
n <- 40
numOfSims <- 1000
```

Now I will generate the data we will use to explore the concepts, below you 
will find the code used to fabricate the data:

```{r}
data <- matrix(rexp(n * numOfSims, lambda), nrow=numOfSims, ncol=n)
data2 <- data.frame(means=apply(data, 1 , mean), sds=apply(data, 1, sd))
```

## Sample Mean v. Theoretical Mean

The Theoretical Mean, mu, of an exponential distribution is given by the 
formula: mu = 1/lambda. Calculating in R will give us the value of mu:

```{r}
mu <- 1/lambda
mu
```

We will calculate the  Sample Mean, x-bar, by using the data we produced. To 
arrive at this value, we will take the mean of the 1000 simulations of the 
means of 40 randomly sampled exponential distributions:

samMean <- mean(data2$means)
samMean

The Sample Mean and Theoretical Mean are quite close!

## Sample Variance v. Theoretical Variance

The Theoretical Standard Deviation, sigma, with rate lambda for a given 
exponential distribution is given to us by the formula: sigma = (1/lambda)/sqrt(n). Calculating in R will give us the value of sigma:

```{r}
sigma <- (1/lambda)/sqrt(n)
sigma
```

The Theoretical Variance, sigma-squared, is given to us by simply taking the 
standard deviation (sigma) and squaring it:

```{r}
sigSquared <- sigma^2
sigSquared
```

Now we will calculate the Sample Variance and the Sample Standard Deviation 
for the purpose of comparison. First the Sample Variance:

```{r}
samVar <- var(data2$means)
samVar
```

Now the Sample Standard Deviation:

```{r}
samSD <- sd(data2$mean)
samSD
```

As we can see, both the the Standard Deviations and Variances are quite 
similar.

## Distribution

To prove the normalcy of the distribution, please reference the below graph:

```{r}
ggplot(data=data2, aes(x=means)) +
geom_histogram(binwidth=0.15, alpha=0.15, aes(y=..density..)) +
stat_function(fun=dnorm, arg=list(mean=mu, sd=sigma), colour="blue")
```

As you can visualize (and conclude) from this graph, not only are the 
Theoretical and Sample Mean and Standard Deviation similar in value, but the 
sample of means has a very similar distribution to a generated normal 
distirbution.